We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-08 paper/paper.tex
edit

We surmount the first difficulty by setting as a point of reference an
spherical satellite distribution and not LCDM simulations. 
This spherical distribution is built from the data itself
(observational or simulated) by randomizing its angular position
around the central galaxy and keeping fixed its radial distance
\citep{2017AN....338..854P}.

We handle the second difficuly by building an analytic probability
distribution that is compatible with the simulated data.
We the use the simulations to estimate the parameters in this
distribution to later use it as a parent sample to generate any
desired number of samples that are by construction statistically
compatible with simulations.

To summarize, simulations help us to construct an explicit probability
distribution for deviations from sphericity for a given LCDM simulated
sample.  
Using this distribution we compute the odds of finding a satellite
distribution that deviates from sphericity as much as the LG does.

In Section we list the sources of the observational and
simulated data to be used throughout the paper.
Next, in Section we describe the methods we use to quantify and
characterize the satellite distributions.
In section we present the results. 
In the discussion section we quantify the correlations between the main
plane properties as described by the simulations.
We use this results to quantify the degree of atipicality of the LG
and estimate the volume that has to probed in simulations in order to
find a pair with a satellite distribution as atipical as the LG. 
Finally, we summarize our conclusions in Section .

@@

For both the M31 and MW we only use the 11 to 15 brightest satellites(using
$M_V$ magnitudes) within a distance of $300$kpc to its central galaxy.
The satellites included for the MW analysis are: 
LMC, SMC, Canis Major, Sagittarius dSph, Fornax, Leo I, Sculptor,
Leo II, Sextans I, Carina, Ursa Minor, Draco, Canes Venatici (I),
Hercules and Bootes II.
The satellites included for the M31 analysis are: Triangulum, NGC205,
M32, IC10, NGC185, NGC147, Andromeda VII, Andromeda II, Andromeda
XXXII, Andromeda XXXI, Andromeda I, Andromeda VI, Andromeda XXIII, LGS 3, 
 and Andromeda III.

>>>>

We surmount the first difficulty by setting as a point of reference an
spherical satellite distribution and not LCDM simulations. 
This spherical distribution is built from the data itself
(observational or simulated) by randomizing its angular position
around the central galaxy and keeping fixed its radial distance
\citep{2017AN....338..854P}. 
We characterize each satellite distribution with its inertia
tensor and summarize the results with the scalars describing the width
of the distribution and their axis ratios.

We handle the second difficuly by building an explicit analytic
probability distribution that is compatible with the simulated data.
We then use the simulations to estimate the parameters in this
distribution to later use it as a parent sample to generate any
desired number of samples that are by construction statistically
compatible with simulations.

To summarize, simulations help us first to construct an explicit probability
distribution for deviations from sphericity for a given LCDM simulated
sample and then, using this distribution, we compute the odds of finding a satellite
distribution that deviates from sphericity as much as the LG does.

In Section we list the sources of the observational and
simulated data to be used throughout the paper.
In Section we describe the methods we use to build halo pairs and 
characterize its satellite distributions.
In Section we present our results to finally present our conclusions
in Section.

@@

For both the M31 and MW we only use the 11 to 15 brightest satellites (using
$M_V$ magnitudes) within a distance of $300$kpc to its central galaxy.
The satellites included for the MW analysis are: 
LMC, SMC, Canis Major, Sagittarius dSph, Fornax, Leo I, Sculptor,
Leo II, Sextans I, Carina, Ursa Minor, Draco, Canes Venatici (I),
Hercules and Bootes II.
The satellites included for the M31 analysis are: Triangulum, NGC205,
M32, IC10, NGC185, NGC147, Andromeda VII, Andromeda II, Andromeda
XXXII, Andromeda XXXI, Andromeda I, Andromeda VI, Andromeda XXIII, LGS 3, 
 and Andromeda III.
